---
title: "Analysis of Average Working Hours and GDP around the world from 1970 - 2017"
author:
- familyname: Wu
  othernames: Zhenyu
  address: Monash Universtidy
  email: zwuu0014@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: Katiyar
  othernames: Harsh
  address: Monash University
  email: hkat0008@student.monash.edu
  correspondingauthor: true
  qualifications: Master of Business Analytics
- familyname: Pan
  othernames: Liwen
  address: Monash University
  email: lpan0037@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: Valensia
  othernames: Josephine
  address: Monash Universtidy
  email: jval0011@student.monash.edu
  correspondingauthor: true
  qualifications: Master of Business Analytics
department: Department of Business and Econometrics
organization: Monash University
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(scales)
```

```{r read-data, echo=FALSE, message = FALSE, warning = FALSE}
Analysis_Data <- read_csv(here::here("Data/Assignment_data.csv"))
```

\section*{Australia and Indonesia}

According to @owidworkinghours, in over 100 years the average working hours has drastically decreased for many countries. However, around the world there are still large gaps between countries where in poorer countries, with lower GDP (Gross domestic product), tend to work much more than workers in richer countries, with higher GDP. Hence, in this section we will look at particularly two countries: Australia (having a higher GDP) and Indonesia (which have a lower GDP).

```{r au_idn, echo=FALSE}
au_idn <- Analysis_Data %>%
  rename(Country = "Entity", 
         awh = "Average annual hours worked by persons engaged (avh) (PWT 9.1 (2019))",
         gdp = "Output-side real GDP per capita (gdppc_o) (PWT 9.1 (2019))") %>%
  select(Country, Year, awh, gdp) %>%
  filter(Country %in% c("Australia", "Indonesia"), 
         Year >=1970 & Year <=2017)
```

```{r awh, echo=FALSE, fig.cap="Comparison of Average annual hours worked by workers in Australia and Indonesia", fig.height= 4}
au_idn %>% 
  ggplot(aes(x = Year, 
             y = awh, 
             color = Country)) +
  geom_line() +
    labs(x = "Year",
         y = "hours",
         title = "Average annual hours worked by workers from year 1970-2017",
         caption = "Data from ourworldindata.org (2020)") +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  theme_bw()
```

The figure \@ref(fig:awh) and figure \@ref(fig:gdp) that show how the Average annual working hours and the GDP change over the year 1970 to 2017 in Australia and Indonesia. From figure \@ref(fig:awh), we can see that Indonesia Average working hours have fluctuated with a significant drop in the mid 1980s and have been increasing for the next few years. While Australia has an overall decreasing trend overtime. 

```{r gdp, echo=FALSE, fig.cap="Comparison of Australia's and Indoensia's GDP per capita", fig.height= 4}
au_idn %>% 
  ggplot(aes(x = Year, 
             y = gdp, 
             color = Country)) +
  geom_line()+
    labs(x = "Year",
         y = "USD",
         title = "GDP per capita from year 1970-2017" ,
         caption = "Data from ourworldindata.org (2020)")+
  scale_y_continuous(labels = label_number(prefix="$", big.mark = ",")) +
  theme_bw()
```

The figure \@ref(fig:gdp) demonstrates that Australia's GDP has risen significantly, while Indonesia's GDP just had a slight increase with a small drop in the late 1990s. From these figures we can see that in spite of  working less hours over the years, Australia's GDP kept increasing while Indonesia's GDP did not grow as much despite having more average working hours.


```{r mean, echo=FALSE}
au_idn %>% 
    group_by(Country) %>%
    summarise(avg_avh = mean(awh),
              avg_gdp = mean(gdp)) %>%
  kable(col.names = c("Country", 
                      "Average of the Average Annual Working Hours (hours)", 
                      "Average of GDP per capita (USD)"),
        caption = "The Comparation of Average Annual Working Hours and GDP between Australia and Indonesia",
        digits = 2,
        align = "lcr") %>%
  kable_styling(full_width = F, 
                bootstrap_options = c("striped", "hover", "condensed"), latex_options = "hold_position")
```

```{r scatter, echo = FALSE, fig.cap = 'Inverse Correlation between Average Annual Working Hours and GDP per capita in Australia and Indonesia', message=FALSE, fig.height= 4}
au_idn %>% 
  ggplot(aes(x = awh, 
             y = gdp, 
             color = Country)) +
  geom_point()+
  geom_smooth()+
    labs(x = "Average Annual Working Hours (hours)",
         y = "GDP per capita (USD)",
         title = "Average Annual Working Hours VS GDP per capita from year 1970-2017" ,
         caption = "Data from ourworldindata.org (2020)")+
  scale_y_continuous(labels = label_number(prefix="$", big.mark = ",")) +
  scale_x_continuous(labels = label_number(big.mark = ",")) +
  theme_bw()
```

Furthermore, looking at the comparison table \@ref(tab:mean) here, we can see that on average from the year 1970 to 2017,  Australia has around 100 Average Working Hours less than Indonesia, but the GDP is 7 times higher compared  to Indonesia's GDP. Therefore we can conclude that between Australia and Indonesia there is an inverse correlation as seen in figure \@ref(fig:scatter), where less Average working hours contributed to higher GDP while more working hours resulted in a lower overall GDP.

\clearpage