---
title: "Analysis of CO2 Emission and Energy Consumption around the world"
author:
- familyname: Wu
  othernames: Zhenyu
  address: Monash Universtidy
  email: zwuu0014@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: Katiyar
  othernames: Harsh
  address: Monash University
  email: hkat0008@student.monash.edu
  correspondingauthor: true
  qualifications: Master of Business Analytics
- familyname: Pan
  othernames: Liwen
  address: Monash University
  email: lpan0037@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: Valensia
  othernames: Josephine
  address: Monash Universtidy
  email: jval0011@student.monash.edu
  correspondingauthor: true
  qualifications: Master of Business Analytics
department: Department of Business and Econometrics
organization: Monash University
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```


\section*{Country China and USA}

## Read data


```{r echo=FALSE, message=FALSE, warning=FALSE}
Analysis_Data <- read_csv(here::here("Data/Assignment_data.csv"))
```




```{r warning=FALSE, message=FALSE}
# filtering data from 1970 to 2017 for China and the United States
data <- Analysis_Data %>%
  filter(Entity %in% c("China","United States")) %>%
  filter(Year>=1970 & Year<=2017)
dim(data)
```

## Overall descriptive statistical analysis
 
```{r warning=FALSE, message=FALSE}
data <- data %>%
  rename(Average.annual.hours.worked=
        "Average annual hours worked by persons engaged (avh) (PWT 9.1 (2019))",
        GDP.per.capita="Output-side real GDP per capita (gdppc_o) (PWT 9.1 (2019))",
        Population="Population (historical estimates)",
        Country=Entity) 
 overall <- data %>%
    group_by(Country) %>%
    summarise_at(c("Average.annual.hours.worked","GDP.per.capita","Population"),
                 list(Minimum = ~min(.,na.rm=TRUE), 
                      Median = ~median(.,na.rm=TRUE), 
                      Mean = ~mean(.,na.rm=TRUE),
                      Maximum = ~max(.,na.rm=TRUE))) %>%
    pivot_longer(!Country, names_sep ="_",
                 names_to = c("Variable", ".value"))%>%
   mutate(Variable=ifelse(Variable=="Average.annual.hours.worked",
                          "Hours.worked",Variable))
```

```{r Table1, warning=FALSE, message=FALSE}
knitr::kable(overall, digits = 2,
    caption = "Descriptive statistical analysis of China and the United States")
```

## Trends in average annual hours worked and GDP per capita

```{r Figure1,fig.cap="Trends in GDP per capita", warning=FALSE, message=FALSE}
ggplot(data,mapping = aes(x = Year,y=GDP.per.capita,
                           color=Country,group=Country)) +
  geom_line() +
  labs(y ="GDP per capita", 
       caption = "Source: World Bank data base")+
    theme_bw()
```

```{r Figure2,fig.cap="Trends in average annual hours worked", warning=FALSE, message=FALSE}
ggplot(data,mapping = aes(x = Year,y=Average.annual.hours.worked,
                           color=Country,group=Country)) +
  geom_line() +
  labs(y ="Average annual hours worked", 
       caption = "Source: World Bank data base")+
    theme_bw()
```

## The relationship between average annual hours worked and GDP

```{r Figure3,fig.cap="Relationship between average annual hours worked and GDP (China)", warning=FALSE, message=FALSE}
data %>%
    filter(Country=="China")%>%
    ggplot(mapping = aes(x = Average.annual.hours.worked,
                          y=GDP.per.capita))+
    geom_point() + 
    stat_smooth(method=lm)+
  labs(x ="Average annual hours worked", 
       y ="GDP per capita", 
       caption = "Source: World Bank data base")+
    theme_bw()
```

```{r Figure4,fig.cap="Relationship between average annual hours worked and GDP (United States)", warning=FALSE, message=FALSE}
data %>%
    filter(Country=="United States")%>%
    ggplot(mapping = aes(x = Average.annual.hours.worked,
                          y=GDP.per.capita))+
    geom_point() + 
    stat_smooth(method=lm)+
  labs(x ="Average annual hours worked", 
       y ="GDP per capita", 
       caption = "Source: World Bank data base")+
    theme_bw()
```


In this section, I analyzed data from China and the United States. First, I filtered out the data for these two countries from 1970 to 2017. Then I performed an overall descriptive statistical analysis of the primary variables (Average.annual.hours.worked, GDP.per.capita and Population).

As shown in Table1\@ref(tab:Table1), the mean or median population in China is significantly larger than in the United States. But in GDP per capita, China is significantly less than the United States. And the average annual hours worked is slightly higher in China than in the United States.

The trends of GDP in China and USA in Figure\@ref(fig:Figure1) shows that GDP per capita in both China and the U.S. is rising year by year, but the upward trend is more obvious in the United States. And for the average annual hours worked shown in Figure\@ref(fig:Figure2), I found a clear upward trend of average annual hours worked in China, while the United States has fluctuated but declined slightly overall.

Finally, I compared the relationship between average annual hours worked and GDP per capita. In The United States Figure\@ref(fig:Figure4), as the annual work hours going down the trend of GDP per capita will going up. But for China Figure\@ref(fig:Figure3) is completely opposite. When the annual work hours going up, The GDP per capital will also going up. I think it due to the high-speed development of economic in China. Furthermore, @BANISTER200521 also mentioned that in 21 of the 24 years from 1978 to 2001, China's per capita GDP grew in real terms between 6% and 14%. China's per capita living standards (measured by real GDP per capita) nearly quadrupled between 1978 and 2001.

# INDIA and UNITED KINGDOM

For **India and United Kingdom**, GDP and Annual working hours data from 1970 to 2017, lets calculate average of GDP and Working hours from 1970 to 2017 in \@ref(tab:TableAvg)


```{r TableAvg, message=FALSE, echo=FALSE, warning=FALSE}
Ind_UK_Data <- Analysis_Data %>%
    filter(Entity %in% c("India", "United Kingdom"), Year >= 1970, Year <= 2017) %>%
    rename(Country = "Entity",
           Avg_Annual_Working_Hours = "Average annual hours worked by persons engaged (avh) (PWT 9.1 (2019))", 
           GDP = "Output-side real GDP per capita (gdppc_o) (PWT 9.1 (2019))", 
           Population = "Population (historical estimates)")

Avg_GDP_WH <- Ind_UK_Data %>%
    group_by(Country) %>%
    summarise(avg_GDP = mean(GDP), avg_working_hrs = mean(Avg_Annual_Working_Hours))

kable(Avg_GDP_WH, caption = "Average GDP and Working hours of India and United Kingdrom from 1970 to 2017", align = "c") %>%
    kable_classic_2(full_width = F) %>%
   kable_styling( position = "center",latex_options = "hold_position")
```


From the above table \@ref(tab:TableAvg), we see that despite India has more average working hours than United Kingdom, the average vale of GDP of United Kingdom is very high than India which means, for India and United Kingdom, GDP does not depend on Working hours solely, there are other factors as well.


To understand this, let's create a figure and see the trend in GDP and average working hours in India and United Kingdom.

```{r FigTrend, message=FALSE, echo=FALSE, warning=FALSE, fig.cap="Average working hours and GDP of India and UK from 1970 to 2017", fig.align='center'}
p1 <- ggplot(Ind_UK_Data, aes(x = Year, 
                        y = Avg_Annual_Working_Hours,
                        color = Country)) + geom_line() +
    ylab("Avg Work Hrs (Annual)") + labs(title = "Avg Work Hrs of India and UK from 1970 to 2017") + theme_bw()



p2 <- ggplot(Ind_UK_Data, aes(x = Year, 
                        y = GDP,
                        color = Country)) + geom_line() + 
    labs(title = "GDP each year of India and UK from 1970 to 2017") + theme_bw()


gridExtra::grid.arrange(p1,p2, nrow=2)

```



From the above Figure \@ref(fig:FigTrend), it is clear that in India, the Average working hours and GDP both are increasing but not as compared to UK. On the other hand, in UK, Average working hours are decreasing continuously while GDP is going up. Therefore, GDP does not solely depend on working hours or we can say that, in richer country, UK, people work for lesser number of hours as compared to India with low GDP. In India, the population has increased to a great extent and in UK, the increase has not been that much, therefore this huge increase in population might be another reason for India's falling short in GDP growth.

To understand GDP further and how the GDP is affected and what are the macroeconomics factors affecting GDP growth, I also read an article @article which discusses about the macroeconomics factors which affect the GDP growth.

# COnclusion

## Reference

[1] Wickham H, Averick M, Bryan J, et al. Welcome to the Tidyverse[J]. Journal of open source software, 2019, 4(43): 1686.

[2] Wickham H, Chang W, Wickham M H. Package ‘ggplot2’[J]. Create elegant data visualisations using the grammar of graphics. Version, 2016, 2(1): 1-189.